Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-20 stp/paper_aaai/main.tex
Backing up everythin

\section{Problem Statement \label{SEC:problem}}
We follow the definitions proposed by Doal \etal{} \cite{doan2012principles}.

@@

An ontology $\mathcal{O}$ is a specification of classes of objects, their 
data properties and relationships between them.
An example of an ontology is given in Fig.~\ref{FIG:onto}. 
A Class in an ontology can have \emph{data properties} or \emph{object properties}. 
For example, an ``Organisation'' has a ``Person'' 
(which is a class with its own properties), and it has a ``name'' (which 
is a data property). 
Also, a Class can be a subclass of another Class. 
For 
example ``Cities'' and ``States'' are both ``Places''. 
A subclass inherits all the properties of the parent class.
\npr{rephrase, I think terminology is off}

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
 We define $\mathcal{N}_m = \mathcal{C}_m \cup 
\mathcal{D}_m$. $ \mathcal{C}_m$ corresponds to classes in the ontology 
$\mathcal{O}$. $\mathcal{D}_m$ corresponds to data 
properties in the ontology. 
The edges in the semantic model correspond to relationships in the ontology, as shown if Fig.~\ref{FIG:onto} and \ref{FIG:sem}.

@@

A \emph{source} $s$ is a $n$-ary relation with a set of attributes 
$\mathcal{A}_s = (a_1,...,a_n)$.

An \emph{attribute mapping} function $\phi : \mathcal{A}_s \mapsto 
\mathcal{D}_m$ is a function which maps the attributes of the source $s$ into the nodes of the semantic model $m$. 
It can be a partial mapping, meaning that only some of the attributes
are connected to the nodes of $m$.

A \emph{source description} is a triple $\delta = (s, m, \phi)$ where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.

Our problem can be stated now the following way. We have an ontology 
$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
(s_l, m_l, \phi_l)\}$.
Given a new source $s^\star$, we want to build a semantic model $m^\star$ and an attribute mapping function $\phi^\star$ such that 
$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source 
description. 
We
use the term ``appropriate'' since there might be many such triples which are well-formed source descriptions, but only one or a few will capture the intended meaning of the source. 
Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} between the semantic model 
$m^\star$ and the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}

@@

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which involves giving a confidence value to a match occurring between an attribute from $s^\star$ and type $l \in 
\mathcal{L_O}$. \ddg{CHECK!}

>>>>

\section{Problem Statement \label{SEC:problem}}

@@

In our work we consider that an ontology $\mathcal{O}$ has such basic elements as classes which represent a set of concepts, literal values, individuals which are members of classes and properties~\cite{Spanos:semweb}.
Properties are classified into object properties, which relate two individuals, and datatype properties, which relate indivuduals to literal values.
An example of an ontology is given in Fig.~\ref{FIG:onto}. 
Here, an individual of the class ``Organisation'' can be related to an individual of the class ``Person'' via object properties ``ceo'' or ``worksFor'', and it can have a data property ``name''. 
We also consider a special ``subclass'' (or ``is-a'') type of object properties.
For 
example, ``Cities'' and ``States'' are both ``Places''. 
A subclass inherits all the properties of the parent class.
\npr{check}

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
 We define $\mathcal{N}_m = \mathcal{C}_m \cup 
\mathcal{D}_m$. $ \mathcal{C}_m$ corresponds to classes in the ontology 
$\mathcal{O}$. $\mathcal{D}_m$ corresponds to data 
properties in the ontology. 
The edges in the semantic model correspond to object properties in the ontology, as shown if Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
The semantic model may have several instances of the same ontology class or object property.

@@

In our setting we work with relational sources.
Hence, a \emph{data source} $s$ is a $n$-ary relation with a set of attributes 
$\mathcal{A}_s = (a_1,...,a_n)$.
We want to map them to the target ontology $\mathcal{O}$.

Following the traditional data integration framework~\cite{doan2012principles}, we decompose the problem into two parts: schema matching and schema mapping.
Schema matching part, which we refer to as \emph{semantic labeling}, finds correspondences between attributes from data sources and data nodes of the target ontology.
In the schema mapping part we want to generate the semantic models of data sources by identifying the connecting paths for the matched data nodes.

An \emph{attribute mapping} function $\phi : \mathcal{A}_s \mapsto 
\mathcal{D}_m$ is a function which maps the attributes of the source $s$ into the nodes of the semantic model $m$. 
It can be a partial mapping, meaning that only some of the attributes
are connected to the nodes of $m$.
The attribute mapping function addresses the first part of the problem (semantic labeling).

We define a \emph{source description} as a triple $\delta = (s, m, \phi)$ where $s$ is a source, $m$ is a semantic model, and $\phi$ is an attribute mapping.
Our problem can be stated now the following way. We have an ontology 
$\mathcal{O}$ and a set of source descriptions $S_T = \{(s_1, m_1, \phi_1),..., 
(s_l, m_l, \phi_l)\}$.
Given a new source $s^\star$, we want to build a semantic model $m^\star$ and an attribute mapping function $\phi^\star$ such that 
$\delta^\star = (s^\star,m^\star,\phi^\star)$ is an \emph{appropriate} source description. 
We use the term ``appropriate'' since there might be many such triples which are well-formed source descriptions, 
but only one or a few will capture the intended meaning of the source. 
Our goal is to automatically build $\delta^\star$ such that it maximizes the \emph{precision} and \emph{recall} between the semantic model 
$m^\star$ and the semantic model $m^\dag$ that the user considers correct. \npr{definitions for precision and recall}

@@

The first step to model the semantics of a new source $s^\star$ is to recognize the semantic types present in the source. 
We call this step \emph{semantic labeling}, which assigns a confidence value to a match of an attribute from $s^\star$ to a type $l \in 
\mathcal{L_O}$.
%\ddg{CHECK!}
